Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-12-14 paper/paper_acm.tex
reduce dense

We now recall the presence of a factorization system in homotopy type
theory, constituted by embeddings and surjections.

@@

  An $n$-subobject of $E$ classified by $\chi$ is said to be {\em
    closed in $E$} if it is equal to its closure, \ie
  $\chi = \modal_n \circ \chi$.
\end{defi}

The definition of a dense $n$-subobject requires more work as the
characteristic function $\chi_E$ of $E$ seen as an $n$-subobject of
itself is not the constant function equal to $\one$, as it is the case
for toposes, but rather the map 
%
\begin{mymath}\chi_E  = \lambda e . \ \sum_{e':E} e=e'.\end{mymath}
%
This means that we need to take more care of the homotopy structure of
this characteristic function, and in particular, the definition of a
dense $n$-subobject comes with an additional coherence condition
(which is trivial when $n=-1$).

\begin{defi}
  Let $E$ be a type, and $\chi:E \to \Type_n$. The $n$-subobject $\iota :
  A \to E$ of $E$
  classified by $\chi$ is {\em dense} in $E$ when its $\modal_n$-closure
  is equivalent to $\chi_E$, \ie
  %
  \begin{mymath}[-0.3em]\prod_{e:E}~ \left(\sum_{e':E} e=e'\right) \simeq \modal_n
  (\chi~e).\end{mymath}
  % 
  % and moreover, for any $x:A$, the following diagram 
  % commutes, 
  % \begin{mymath}\xymatrix{
  %   \sum_{e':A} x = e' \ar@{=}[r] \ar[d]_{\iota'} & (\chi \ x)
  %   \ar[d]^{\eta_{(\chi \ x)}}\\
  %   \sum_{e':E} x = e' \ar@{=}[r] & \modal_n (\chi \ x)
  % }\end{mymath}
  % where $\iota': x \mapsto (\iota (\pi_1 x) ; \pi_2 x)$.
\end{defi}

@@

\begin{defi}
  For any type $A$ and $E$, $\iota : A \to E$ and $F:\Type_{n+1}$, we define
    $\Phi_E^\iota \defeq \cdot \circ \iota : (E \to F) \to (A \to F) $
    as the map sending an  arrow $f:E\to F$ to its restriction $f \circ \iota$.
  % \item if $A \to E$ with $n$-truncated homotopy fibers, $\Phi_E^\chi$ is the
  %   map sending $f:~E \to f$ to $\restriction f A$.
  % \end{itemize}
\end{defi}

>>>>

\kq{Maybe delete this subsection?}
We now recall the presence of a factorization system in homotopy type
theory, constituted by embeddings and surjections.

@@

  An $n$-subobject of $E$ classified by $\chi$ is said to be {\em
    closed in $E$} if it is equal to its closure, \ie
  $\chi = \modal_n \circ \chi$.

  An $n$-subobject of $E$ classified by $\chi$ is said to be {\em
    dense in $E$} if its closure is $E$, \ie
  $\modal_n \circ \chi = \lambda e. 1$ 
\end{defi}

% The definition of a dense $n$-subobject requires more work as the
% characteristic function $\chi_E$ of $E$ seen as an $n$-subobject of
% itself is not the constant function equal to $\one$, as it is the case
% for toposes, but rather the map 
% %
% \begin{mymath}\chi_E  = \lambda e . \ \sum_{e':E} e=e'.\end{mymath}
% %
% This means that we need to take more care of the homotopy structure of
% this characteristic function, and in particular, the definition of a
% dense $n$-subobject comes with an additional coherence condition
% (which is trivial when $n=-1$).

% \begin{defi}
%   Let $E$ be a type, and $\chi:E \to \Type_n$. The $n$-subobject $\iota :
%   A \to E$ of $E$
%   classified by $\chi$ is {\em dense} in $E$ when its $\modal_n$-closure
%   is equivalent to $\chi_E$, \ie
%   %
%   \begin{mymath}[-0.3em]\prod_{e:E}~ \left(\sum_{e':E} e=e'\right) \simeq \modal_n
%   (\chi~e).\end{mymath}
%   % 
%   % and moreover, for any $x:A$, the following diagram 
%   % commutes, 
%   % \begin{mymath}\xymatrix{
%   %   \sum_{e':A} x = e' \ar@{=}[r] \ar[d]_{\iota'} & (\chi \ x)
%   %   \ar[d]^{\eta_{(\chi \ x)}}\\
%   %   \sum_{e':E} x = e' \ar@{=}[r] & \modal_n (\chi \ x)
%   % }\end{mymath}
%   % where $\iota': x \mapsto (\iota (\pi_1 x) ; \pi_2 x)$.
% \end{defi}

@@

\begin{defi}
  For any type $A$ and $E$, $\iota : A \to E$ and $F:\Type_{n+1}$, we define
    $\Phi_E^\iota \defeq - \circ \iota : (E \to F) \to (A \to F) $
    as the map sending an  arrow $f:E\to F$ to its restriction $f \circ \iota$.
  % \item if $A \to E$ with $n$-truncated homotopy fibers, $\Phi_E^\chi$ is the
  %   map sending $f:~E \to f$ to $\restriction f A$.
  % \end{itemize}
\end{defi}
